The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-13 document/ms.tex

\begin{floattable}
\begin{deluxetable}{cccc}
\tabletypesize{\footnotesize}
\caption{The inferred parameters for the long-period transiting exoplanet
candidates \label{tab:masses}}
\include{masstab}
\tablenotetext{*}{The equilibrium temperature is computed assuming zero
albedo.}
\end{deluxetable}
\end{floattable}

>>>>

\begin{floattable}
\begin{deluxetable}{cccc}
\tabletypesize{\footnotesize}
\caption{The mass and semi-major axis estimates for the candidates from
Table~\ref{tab:catalog} \label{tab:masses}}
\include{masstab}
\tablenotetext{*}{The mass is estimated based on the measured radius using a
probabilistic mass--radius relation \citep{Chen:2016}.}
\end{deluxetable}
\end{floattable}
